### 2013-07-24 doc/asplos14/intro.tex
new data, partial characterization

Our evaluation of \Grappa shows that its core components provide scalable performance for irregular applications.  It can multiplex thousands of workers on a multicore CPU and is limited only by DRAM bandwidth, not latency, to fetch worker state.  The communication layer helps \Grappa achieve over 1 billion random updates per second across 64 system nodes. \TODO{update with new performance numbers}.
% Comparing \Grappa and native MPI implementations for more complex kernels is nuanced. Some applications use MPI in a straightforward manner, such as GUPS, PageRank, and Unbalanced Tree Search, for which \Grappa is 2-5X faster. On the other hand, some MPI implementations of irregular applications recognize its limitations and are written specially to aggregate messages and do some communication asynchronously, performing much the same work \Grappa does behind the scenes, but without paying the cost of generality imposed by context switches or message serialization, to name a few. We see this in our comparisons for Breadth First Search and Integer Sort, where the MPI implementation is \checkme{6-10X} faster.

%When we compare \Grappa to the custom Cray XMT, we find \Grappa to be between 2.6X faster and 4.3X slower depending on the benchmark.
% \TODO{appA and tuned compared to appB and untuned is not ideal}

>>>>

Our evaluation of \Grappa shows that its core components provide scalable performance for irregular applications. It can multiplex thousands of workers on a multicore CPU and is limited only by DRAM bandwidth, not latency, to fetch worker state.  The communication layer helps \Grappa achieve over 1 billion random updates per second across 64 system nodes. \Grappa provides performance approaching and in some cases exceeding that of the custom-hardware XMT, as well as MPI and UPC implementations of the same benchmarks. When we compare \Grappa to the XMT, we find \Grappa to be between 2.6X faster and 4.3X slower depending on the benchmark. When compared with MPI and UPC, \Grappa is between 11X faster and 5.4X slower depending on the benchmark. We find that the benchmarks that are faster contain specialized implementations of features \Grappa provides generally.
